Verifying Spatial Properties of Array Computations

### 2017-04-16 oopsla17/algorithms.tex
fix enumerate

\begin{enumerate}[leftmargin=1.5em]
A covering of (possibly overlapping) regions is computed iteratively
by the following steps until a fixed-point is reached:

\begin{enumerate}

\item \textbf{Coalesce intervals}
Intervals which are adjacent (contiguous in one dimension) are
coalesced.

\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_j(S')$ such that $|S| = |S'| + 1$.
\end{defn}
%

\begin{definition}[Contiguous]

\end{definition}

\item \textbf{Remove completely overlapped intervals}

\item \textbf{Covering}

>>>>

\begin{enumerate}[leftmargin=1.5em]
\item
A covering of (possibly overlapping) regions is computed iteratively
by the following steps until a fixed-point is reached:

\begin{enumerate}
\item \textbf{Coalesce intervals}
Intervals which are adjacent (contiguous in one dimension) are
coalesced.

\begin{defn}{[Contiguous]}
  An index scheme
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_j(S')$ such that $|S| = |S'| + 1$.
\end{defn}
%
\item \textbf{Remove completely overlapped intervals}
\item \textbf{Covering}
\end{enumerate}
\end{enumerate}
